---
title: "Example1"
author: "Dr. Debasish Mukherjee"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initialize data set

Loading inbuilt `iris` data set to perform some analysis

```{r LoadingData}
## Load data
data("iris")
```

First have a look, how the data is arranged.

```{r DataView}
# I'm not sure what's in the iris data. I'm printing it below to take a look
head(iris)

```

## Data analysis

Now we have an idea how the data is arranges. Let's have a closer look to get more idea about the dataset.

-   What are the means of the parameters
-   How the data is distributed?
-   Is there a significant difference of a parameter across species?

Let's calculate mean

```{r mean}

# Below, we calculate the average Sepal.Length across all Species in the mtcars data frame.
print(paste0("Average of Sepal Length : ", mean(iris$Sepal.Length)))
```

Let's have look how one parameter is distributed against another.

## Plot

```{r ScatterPlot}
# Here, we also plot Petal.Length against Sepal.Length.
plot(iris$Petal.Length, iris$Sepal.Length, pch=19, col=1)

```

Here we are comparing the mean of Petal Length across Species

```{r BarPlot}

# Typical barplot to check the mean of Petal.Length across species
df = aggregate(iris[,1:4], by = list(iris$Species), FUN = mean)
barplot(Petal.Length~Group.1, data = df,xlab = c('Species'), ylab = c('Petal Length'), col=c(1:3))
```

Let's have look on the distribution

```{r BoxPlot}
# Here, we plot Petal.Length across Species to check the distribution
boxplot(Petal.Length ~ Species, data = iris, col=c(1:3))

```

## Some Statistics

Let's check if there is a significant difference of a parameter between two species.

```{r t-test}
# Subset data
setosa <- iris[iris$Species == "setosa", ]
versicolor <- iris[iris$Species == "versicolor", ]

# Run t-test
t.test(x = setosa$Petal.Length, y = versicolor$Petal.Length)

```

### References

```{r}
sessionInfo()
```

------------------------------------------------------------------------

## Heading1

### Heading2

dskndnc df 

```{r eval=TRUE, echo=FALSE}
tail(iris)
```

